---
title: "Creating an interactive map of our sample sites"
output:
  html_document:
    df_print: paged
  pdf_document: default
---
Here, I have created an interactive map of our sample collection sites using the mapping file. First I'm going to install some packages and access its library.
```{r}
install.packages("leaflet", repos = "http://cran.us.r-project.org")
library(leaflet)
library(sp)
```

Next I'm going to retrieve the mapping file, and store it in the variable 'data'.
```{r}
data <- read.csv("allyears_map_corrected.csv")
```

Now I'm going to make sure the contents of the longitude/latitude columns are numeric.
```{r}
data$SampleLongitude <- as.numeric(data$SampleLongitude)
data$SampleLatitude <- as.numeric(data$SampleLatitude)
```

I've created a new SpatialPoints dataframe, and inside of this function I am telling R which columns to find the lattitude (first number) and longitude (second number) from the mapping file (which I have represented as 'data').
```{r}
data.SP <- SpatialPointsDataFrame(data[,c(8,9)], data[,-c(8,9)])
```

Now I'm going to add the markers.
```{r}
m <- leaflet() %>% addTiles() %>%
  addCircleMarkers(data = data, lng = ~SampleLongitude, lat = ~SampleLatitude, popup = ~X.SampleID)
```

Now for the part you've all been waiting for. Running m generates an interactive mapping file. You can click on the points to see which SAMPLEID they belong to.
```{r}
m %>% addProviderTiles(providers$CartoDB.Positron)
```
